IJAR Bayesian Nonparametrics Special Issue Manuscript

### 2015-09-29 ijar-npb-ms.tex
some more stuff

@@

As shown in Walter \& Augustin (2009),
we can have both tractability and meaningful reaction to prior-data conflict
by using sets of priors $\MktZ$ produced by parameter set $\PktZ = [\nktzl, \nktzu] \times [\yktzl, \yktzu]$. 
Then we will have wider intervals for $\Rsys(t)$ in case of prior-data conflict.

@@

>>>>

***e.g., what to do in extreme tail of component distributions?
How sensitive is the method to choosing prior (lower, upper) mean zero for $p^k_t$ at high $t$'s?***

@@

As shown in Walter \& Augustin (2009),
we can have both tractability and meaningful reaction to prior-data conflict
by using sets of priors $\MktZ$ produced by parameter set $\PktZ = [\nktzl, \nktzu] \times [\yktzl, \yktzu]$. 
For such a rectangular prior parameter set $\PktZ$,
the posterior parameter set $\PktN$ is not rectangular anymore.

In case of no prior-data conflict ($s^k_t/n^k_t \in [\yktzl, \yktzu]$),
the set shrinks in the $\ykt$ dimension
(how much it shrinks depends on $\nktz$, leading to the so-called spotlight shape),
leading to smaller $\Rsys(t)$ intervals.

In case of prior-data conflict ($s^k_t/n^k_t \not\in [\yktzl, \yktzu]$),
$\PktN$ has the so-called banana shape,
giving a wider $\yktn$ interval as compared to the non-conflict case. 
As a consequence, we will have wider intervals for $\Rsys(t)$ in case of prior-data conflict.

@@

***Will ask Simme Douwe Flapper (Prof at TU Eindhoven) for real-world example,
otherwise some toy example will do.***

Show $\Rsys(t)$ intervals for prior-data conflict and non-conflict data
to show effect of prior-data conflict.

Show the effect of extra redundancy on $\Rsys(t)$ intervals like in Risk Analysis paper,
or show effect of replacement of failed components in a system
(replaced components constitute a new type with shifted component reliability function)
